### 2018-06-25 latex/figurelegends.tex
first draft figure legends

The substrate affinity of NNMT and NamPRT have opposite effects on NAD consumption (A) and concentration (B), as would be expected. The affinities previously measured for human enzymes (indicated by a black asterisk) appear to be close to optimal, as further improvements would have little or no effect on NAD consumption or concentration.

@@

Deuterostomia that encode NNMT show a sequence insertion in the N-terminal region of NamPRT. A) Multiple sequence alignment of NamPRT of selected deuterostomes show a sequence insertion in organisms that encode NamPRT and NNMT. Coloured circles indicate the enzymes present in the species; blue: NamPRT and NNMT; black: NamPRT, NADA, and NNMT; yellow: NamPRT and NADA.

B) The inserted region is not resolved in crystal structures of human NamPRT and thus appears to be a flexible loop structure at the surface of the NamPRT dimer, coloured in red. The visualisation is based on a structure prediction of SWISS-MODEL \cite{Arnold2006,Biasini2014} of the sequence of the human NamPRT (P43490) using the model 2H3D as template \cite{Wang2006}.

\subsection{Figure 7}

>>>>

\textbf{The substrate affinities of human NNMT and NamPRT are optimal}. Both  NAD consumption (A) and NAD concentration (B) are increasing with decreasing $K_M$ of NamPRT but decreeasing $K_M$ of NNMT. The affinities reported for human enzymes (indicated by a black asterisk) appear to be close to optimal, as further improvements would have little or no effect on NAD consumption or concentration.

@@

\textbf{The function of the structurally unresolved loop structure of NamPRT} Most deuterostomia that encode NNMT show a sequence insertion in the N-terminal region of NamPRT that has been revealed by multiple sequence alignment of NamPRT from different species (A). Coloured circles indicate the enzymes present in the species; blue: NamPRT and NNMT; black: NamPRT, NADA, and NNMT; yellow: NamPRT and NADA. The inserted region is not resolved in crystal structures of human NamPRT and thus appears to be a flexible loop structure at the surface of the NamPRT dimer, coloured in red  (B) . The visualisation is based on a structure prediction of SWISS-MODEL \cite{Arnold2006,Biasini2014} of the sequence of the human NamPRT (P43490) using the model 2H3D as template \cite{Wang2006}.  The localisation of the FLAG-tagged mutant protein is not changed (E) compared to NamPRT-wildtype. Both show a heterogenous nuclear cytosolic localisation in immunofluerescence images in .... cells (C). But, in vitro measurements using recombinant protein show  that a mutant of NamPRT missing this insertion has lower activity (D)  and is not activated by ATP (E).

\subsection{Figure 7}
\textbf{NNMT provides a competitive advantage and makes NADA obsolete} To simulate competition for common resources we created a two compartment model, where one compartment contained NADA but no NamPRT and one compartment contained NamPRT either with or withour NNMT but no NADA. In the absence of NNMT (A-B) the compartment containing NADA has slightly lower NAD-consumption rates (A) but much higher NAD concentrations (B)  In the presence of NNMT, however, both NAD consumption (C) and NAD concentration (D) are lower in the NADA compartment, but this effect is only observed at low NamPRT $K_M$.
